Paper Visualization

### 2024-09-02 Scripts - Data Cleaning and Visuals/Paper Visualizations.Rmd
changes

```{python Python Load Libraries, Directories, and Datasets}
import os
import pandas as pd
import matplotlib.pyplot as plt
import seaborn as sns
import numpy as np
import plotly.express as px
import plotly.graph_objects as go
import networkx as nx
import scipy

@@

```{r How Many Topics, eval=FALSE, include=FALSE}
# Optimize LDA to find the best number of topics
set.seed(123)
result <- FindTopicsNumber(
  dtm,
  topics = seq(from = 2, to = 10, by = 1),  # Narrow topic range for faster computation
  metrics = c("Griffiths2004", "Deveaud2014"),  # Use fewer metrics
  method = "Gibbs",
  control = list(seed = 123, iter = 500),  # Fewer iterations for quicker results
  mc.cores = 6L,
  verbose = TRUE
)

# Plot results to determine the optimal number of topics
FindTopicsNumber_plot(result)
```

>>>>

```{python Python Load Libraries, Directories, and Datasets, eval=FALSE, include=FALSE}
import os
import pandas as pd
import matplotlib.pyplot as plt
import seaborn as sns
import numpy as np
import plotly.express as px
import plotly.graph_objects as go
import networkx as nx
import scipy

@@

```{r How Many Topics, eval=FALSE, include=FALSE}
# Optimize LDA to find the best number of topics
set.seed(123)
result <- FindTopicsNumber(
  dtm,
  topics = seq(from = 2, to = 10, by = 1),  # Narrow topic range for faster computation
  metrics = c("Griffiths2004", "Deveaud2014"),  # Use fewer metrics
  method = "Gibbs",
  control = list(seed = 123, iter = 500),  # Fewer iterations for quicker results
  mc.cores = 6L,
  verbose = TRUE
)
```

```{r Plot How Many Topics}
# Plot results to determine the optimal number of topics
FindTopicsNumber_plot(result)
```
